INTELLIGENT SYSTEMS

### 2021-04-07 paper_5.tex
finish 5.3.4

>>>>

\subsubsection{Modality Fusion}
The merging of data that occurs at the input is useful for increasing the accuracy of the 
network and allows understanding the relationships between 
the different types of input data. Each data coming from a specific sensor 
will be inserted in an individual branch, composed of a specific number of 
convolutional layers that will calculate specific predictors for each sensor. 
In the end, the data will be concatenated in a common branch which has the 
task of extracting the combined features from all the sensors. Based on the accuracy metric, the 
layer that will return the best result will be selected.

\subsubsection{Identity Authentication}
